Open Data, Open Source and Open Standards in chemistry - The Blue Obelisk five years on

### 2011-05-12 paper.tex
Shorten indigo and brunn text, and add webref for brunn

Two new Open Source cheminformatics toolkits have appeared since the
original paper. In 2006 Rational Discovery, a cheminformatics service
company (since closed down), released RDKit \cite{WebRDKit} under the
BSD License. RDKit continues to be actively developed and includes
code donated by Novartis.

More recently, GGA Software Services (a contract programming company)
released the Indigo toolkit \cite{WebIndigo} and associated software
in 2009 under the GPL. Indigo is written from scratch in C++ and has
high-level wrappers for using it in C, Java, Python, or .NET
environment. Like other toolkits, Indigo provides support for
tetrahedral and cis-trans stereochemistry, 2D coordinate generation,
exact/substructure/SMARTS matching, fingerprint generation (all these
both for molecules and reactions), and canonical SMILES computation.
It also provides some less common functionality, like matching
tautomers and resonance substructures, enumeration of subgraphs,
finding maximum common substructure of $N$ input structures, and
enumerating reaction products. Indigo also has its rendering plugin,
which is used in a lot of commercial and open-source projects as the
main 2D chemical rendering engine.

@@

Bioclipse~\cite{Spjuth:2007fk} (v2.4 released in Aug 2010) and Avogadro
\cite{WebAvogadro} (v1.0 in Oct 2009) are two examples of such software, based
on the CDK and Open Babel, respectively. Bioclipse is an award-winning
molecular workbench for life sciences with a dynamic plugin architecture, and
which wraps cheminformatics functionality behind user-friendly interfaces and
graphical editors. All functionality in Bioclipse is completely scriptable
using an integrated high-level language called Bioclipse Scripting Language
(BSL), which can be used for scripted research or to automate complex
tasks~\cite{Bioclipse2}. Bioclipse in turn acts as base for other software
such as Brunn~\cite{Brunn}, which is a laboratory information system for
microplate based high-throughput screening. Brunn provides a grahical interface
for handling different plate layouts and dilution series. It can automaticly
generate dose response curves and calculate IC$_{50}$-values. In this manner
open source projects empower other open source projects.

>>>>

Two new Open Source cheminformatics toolkits have appeared since the
original paper. In 2006 Rational Discovery, a cheminformatics service
company (since closed down), released RDKit \cite{WebRDKit} under the
BSD License. This is a C++ library with Python and (more recently)
Java bindings. RDKit is actively developed and includes
code donated by Novartis. Recent developments include the Java
bindings, as well as performance improvements for its database
cartridge. More recently, GGA Software Services
(a contract programming company)
released the Indigo toolkit \cite{WebIndigo} and associated software
in 2009 under the GPL. Indigo is a C++ library with
high-level wrappers in C, Java, Python, and the .NET
environment. Like RDKit and other toolkits, Indigo provides support for
tetrahedral and cis-trans stereochemistry, 2D coordinate generation,
exact/substructure/SMARTS matching, fingerprint generation, and
canonical SMILES computation.
It also provides some less common functionality, like matching
tautomers and resonance substructures, enumeration of subgraphs,
finding maximum common substructure of $N$ input structures, and
enumerating reaction products.

@@

Bioclipse~\cite{Spjuth:2007fk} (v2.4 released in Aug 2010) and Avogadro
\cite{WebAvogadro} (v1.0 in Oct 2009) are two examples of such software, based
on the CDK and Open Babel, respectively. Bioclipse is an award-winning
molecular workbench for life sciences with a dynamic plugin architecture, and
which wraps cheminformatics functionality behind user-friendly interfaces and
graphical editors. All functionality in Bioclipse is completely scriptable
using an integrated high-level language called Bioclipse Scripting Language
(BSL), which can be used for scripted research or to automate complex
tasks~\cite{Bioclipse2}. Bioclipse in turn acts as base for other software
such as Brunn~\cite{WebBrunn}, a laboratory information system for
microplate based high-throughput screening. Brunn provides a grahical interface
for handling different plate layouts and dilution series and can automaticly
generate dose response curves and calculate IC$_{50}$-values.
